\documentclass{article}
\usepackage[hidelinks]{hyperref} %for hyperlinks
\usepackage{graphicx} %for images
\usepackage[backend=biber, style=apa]{biblatex} %bibliography
\addbibresource{references.bib}

\hypersetup{
    colorlinks   = true, %Colours links instead of ugly boxes
    urlcolor     = blue, %Colour for external hyperlinks
    linkcolor    = blue, %Colour of internal links
    citecolor   = red %Colour of citations
  }

\title{Web Application Project}
\author{Richard Hughes}
\date{October 9, 2024 - \today}


\begin{document}
\maketitle
\newpage

%TODO: Add the admin page logins
\section*{Preface}
  The development history spans across two GitHub repositories: 
  \href{https://github.com/richardh05/Web-Application-Development-J110823}{my first attempt} and 
  \href{https://github.com/richardh05/Carlos-Pizza}{my final attempt}.
  The reasoning for this will be detailed in the report, and I will attempt to merge the commit history of the former with the latter when I'm more proficient with Git. The database can be accessed with the credentials 
  \verb|user_db_2326227_carlosdb| \& \verb|ID398jQIPoBokrfW|, 
  as well as the admin page of the website with the credentials. The project can be viewed as a \href{https://2326227.win.studentwebserver.co.uk/CO5227}{live webpage} via Plesk.

\tableofcontents
\newpage


\section{Testing}
  \subsection{My project}
  \begin{center}
    \begin{tabular}{|c|c|c|}
      \hline
      cell1dfsdfs & cell2 & cell3 \\
      \hline 
      cell4 & cell5 & cell6 \\  
      cell7 & cell8 & cell9 \\ 
      \hline
    \end{tabular}
    \end{center}
  \subsection{X's project}
  \subsection{X's project}


\section{Development Log}
  \subsection{Homepage \& styling}
    I have created the project, chosen the theme, developed the navigation bar, created all page files, created the logo and styled the template page. More or less everything that was attempted, besides some nitpicks with the styling, is working well. Things that could be improved include the favicon, changing text in the navigation bar and positioning of the footer. I am currently using workarounds for these. \cite{CarlosCSS}
  \subsection{Displaying items}
  \subsection{Adding, deleting \& editing items}
    Due to continued personal issues and other assignments requiring my attention, I’ve been unable to continue with the web application. These issues will be clearing up soon with the four assignments of January ending on the 23rd, at which point I will be able to place all my focus into the programming-heavy projects at the tail end of the year.
  \subsection{Registration \& logins}
    
\printbibliography[heading=bibnumbered]
\end{document}